### 2020-02-18 thesis/paper.tex
fixes

After selecting a file the index of cluster labels can be defined, if labels should be loaded from the file. Otherwise the value can be left at $-1$ indicating that no columns should be used for label information. ``$-2$'' may be also be specified, it is used as a shortcut for selecting the last column as cluster labels, removing the need to count columns if it is the last one. The chosen column is then not inserted as a dimension in the data space but used as the cluster labels, which the color of the loaded points will reflect in the scatter plot of the data-view.

@@

Alternatively, the user can also create a data-set himself from within the tool. It is possible to draw points onto the canvas when the ``SinglePoint'' option is selected in the top right, as in Figure \ref{fig:data-view}. For this, the user only needs to click wherever he wants points placed. It is important to note that if there are more than two dimensions all values for the not shown dimensions will not be set, which may cause a problem for the clustering algorithms later on. Another possibility is the use of the ``ELKIGenerator'', which accepts a XML-style input for defining how to generate data. The definition for this format can be found in corresponding definitions file on the ELKI Github repository \cite{elkixml} or in the tools lib folder. This generator allows defining distributions on dimensions, the number of points for each generated distribution and many additional things like plane rotations. This can be quite useful when wanting to work with a quick sample data-set. In Figure \ref{fig:loaded-data} one can see how the data-view looks when data with cluster labels is shown.

\begin{figure}[h]
	\centering
	\includegraphics[scale=.45]{unob}
	\caption{Data-View with example data-set (including cluster labels)}
	\label{fig:loaded-data}
\end{figure}

@@

@@

@@

For ease of use, workflows can be saved and loaded in the workflow-view, usind the ``Save Wf'' and ``Load Wf'' buttons respectively. The tool creates custom Clustering Workflow Files (CWF) for this, allowing to re-use and modify workflows throughout multiple executions of the tool.

@@

\section{Meta-View and Consensus Clustering}
With either a clustering result loaded in or clustering algorithms run and the meta-clustering performed the meta-view is shown (Figure \ref{fig:meta-view}).

@@

The meta-view consists of five visual elements and some UI-elements in the top. Of the five elements, the left four visualizations give an overview of the data on an individual clustering and meta-level and the right part can be used to filter the base clusterings.

@@

When this button is pressed, if the consensus function supports it a window opens, allowing the user to set a number of desired clusters in the output or to leave this field empty when the function should try to find this parameter itself (Figure \ref{fig:choosek_window}).

@@

The default implemented distance measures are Variation of Information and Clustering Error. 
%%%%%%%%%%%%more

@@

\section{Unobtainable Solutions}
Single clustering algorithms may not be able to find the structure of a data-set when multiple different kinds of structures are present for individual clusters. Combining results of different clustering algorithms may solve this problem, as correctly identified structures should be robust throughout multiple runs of a fitting algorithm while they should not be robust whenever the algorithm doesn't fit the structure. To illustrate this a data-set was created combining a U-shaped density based cluster with Gaussian clusters with different deviations, see Figure \ref{fig:unob}.

>>>>

After selecting a file the index of cluster labels can be defined, if labels should be loaded from the file. Otherwise the value can be left at $-1$ indicating that no columns should be used for label information. ``$-2$'' may be also be specified, it is used as a shortcut for selecting the last column as cluster labels, removing the need to count columns if it is the last one. The chosen column is then not inserted as a dimension in the data space but used as the cluster labels, which the color of the loaded points will reflect in the scatter plot of the data-view. In Figure \ref{fig:loaded-data}, one can see how the data-view looks when data with cluster labels is shown. The data-set used for this example is the same one as in Section \ref{sec:unob}.

\begin{figure}[H]
	\centering
	\includegraphics[scale=.45]{unob}
	\caption{Data-View with example data-set (including cluster labels)}
	\label{fig:loaded-data}
\end{figure}

@@

Alternatively, the user can also create a data-set himself from within the tool. It is possible to draw points onto the canvas when the ``SinglePoint'' option is selected in the top right, as in Figure \ref{fig:data-view}. For this, the user only needs to click wherever he wants points placed. It is important to note that if there are more than two dimensions all values for the not shown dimensions will not be set, which may cause a problem for the clustering algorithms later on. Another possibility is the use of the ``ELKIGenerator'', which accepts a XML-style input for defining how to generate data. The definition for this format can be found in corresponding definitions file on the ELKI Github repository \cite{elkixml} or in the tools lib folder. This generator allows defining distributions on dimensions, the number of points for each generated distribution and many additional things like plane rotations. This can be quite useful when wanting to work with a quick sample data-set.

@@

An example for this view can be seen in Figure \ref{fig:scatter_matrix} with the data-set from Figure \ref{fig:loaded-data}. Here the kernel density estimations also already show a quite clear structure for the yellow and the blue cluster as each of those clusters nicely shows a Gaussian distribution in one dimension.

\begin{figure}[h]
	\centering
	\includegraphics[scale=.25]{scatter_matrix}
	\caption{Scatter Plot Matrix for data-set from Figure \ref{fig:loaded-data}}
	\label{fig:scatter_matrix}
\end{figure}

@@

%%%%%%%%%%%more text somewhere here

@@

For ease of use, workflows can be saved and loaded in the workflow-view, usind the ``Save Wf'' and ``Load Wf'' buttons respectively. The tool creates custom Clustering Workflow Files (CWF) for this, allowing to re-use and modify workflows throughout multiple executions of the tool. This can be especially useful when working with standardized data, such that the parameter ranges are similar or when k-Means is sampled. As this file does not depend on or reference a specific data-set, if may be used for different ones.

@@

\section{Meta-View and Consensus Clustering}
With either a clustering result loaded in or clustering algorithms run and the meta-clustering performed the meta-view is shown.

%%%%%%%%%%possibly more paragraph below
The meta-view consists of five visual elements and some UI-elements in the top. Of the five elements, the left four visualizations give an overview of the data on an individual clustering and meta-level and the right part can be used to filter the base clusterings.

@@

@@

When this button is pressed, a dialog window opens if the consensus function supports defining the number of clusters in the result. With this, the user can define this parameter to force this number of cluster or can leave this field empty when the function should try to estimate this parameter itself (Figure \ref{fig:choosek_window}).

@@

If the requirements of a metric are not fulfilled the measure can only be used as an estimate and may produce unsatisfying clusterings. The default implemented measures are Variation of Information and the Clustering Error.

Variation of Information (VI) \cite{10.1007/978-3-540-45167-9_14} measures how much information is gained/lost when changing a clustering to another. It considers relationships between points and their clusters instead of the relationship between two points and is closely related to the mutual information measure. Unlike mutual information, VI is a metric and can therefor be used as a distance measure here.

Clustering Error (or classification error) \cite{MEILA2007873} represents the fraction of misclassified points assuming one clustering represents the labels of the truth. To compute this the clusters first need to be mapped to one another such that a maximum overlap is obtained in a confusion matrix, i.e. finding a permutation where diagonal entries are maximal. To do this Kuhn’s Hungarian method \cite{Kuhn2010} is used and the diagonal elements of the matrix are summed up. This gives us the number of points for which the two solutions agree, which is subtracted from the total number of points. The resulting value is then divided by the total number of points giving us the desired fraction.
%%%% metric????
%%%%https://publikationen.bibliothek.kit.edu/1000011477/812079

@@

\section{Unobtainable Solutions}\label{sec:unob}
Single clustering algorithms may not be able to find the structure of a data-set when multiple different kinds of structures are present for individual clusters. Combining results of different clustering algorithms may solve this problem, as correctly identified structures should be robust throughout multiple runs of a fitting algorithm while they should not be robust whenever the algorithm doesn't fit the structure. To illustrate this a data-set was created combining a U-shaped density based cluster with Gaussian clusters with different deviations, see Figure \ref{fig:unob}.
